---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mapmaryland

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The goal of mapmaryland is to ease access to spatial data for Maryland at both the local, regional, and statewide level.

## Installation

You can install the development version of mapmaryland like so:

``` r
# pak::pkg_install("elipousson/mapmaryland")
```

## Example

```{r}
library(mapmaryland)
```

Currently, the package has a limited number of data access functions, prepackaged datasets, and reference data with an index of Maryland ArcGIS services.

```{r}
dplyr::glimpse(md_arcgis_index)
```


```{r get_md_tigris}
location <-
  get_md_tigris(
    name = "Hyattsville",
    type = "census places"
  )

location
```

```{r get_imap_data}
streams <-
  get_water_data(
    location = location,
    type = "streams"
  )

plot(streams, max.plot = 1)
```
